Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-05-22 manuscript-figures.Rmd
add vector trait TPC dataset

data.in.transform <- read_rds(here::here("data/clean/TPC_param_samples.rds"))

@@

```{r load-data, include=FALSE}
# Run analysis scripts to obtain data for plotting -----------------------------

# # Define temperature range of study
# Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301
# 
# # Thin sample size
# thin_size <- 1000 # full = 1000, thin = 100
# 
# plot_bool = FALSE
# source("code/trait-transform.R", local = TRUE)
# # Host density vector: Number of values to include to consider for vertebrate host density
# KH_vec_length <- 300 # full = 300, thin = 20
# 
# # Biting tolerance vector: Number of values to consider for biting tolerance
# sigmaH_vec_length <- 300 # full = 300, thin = 20
# 
# # Get data for plotting thermal performance curves (data.Vec)
# !!! save a specific dataset to use for plotting trait TPCs
# source("code/trait-variation.R", local = TRUE)

# Load output data -------------------------------------------------------------
# These data are produced by the code in code/get-outputs.R

# R0 data # !!! needs to be updated to include 1e-1, 1e0, 1e1
data.R0 <- read_rds("results/R0_vals.rds")
# Topt data
data.Topt <- read_rds("results/Topt_vals.rds")
# Critical thermal extrema data
data.CT <- read_rds("results/CT_vals.rds")

>>>>

@@

```{r load-data, include=FALSE}
# Load results data -------------------------------------------------------------
# Vector trait TPC data
data.Vec <- read_rds("results/VecTPC_vals.rds")
# R0 data # !!! needs to be updated to include 1e-1, 1e0, 1e1
data.R0 <- read_rds("results/R0_vals.rds")
# Topt data
data.Topt <- read_rds("results/Topt_vals.rds")
# Critical thermal extrema data
data.CT <- read_rds("results/CT_vals.rds")
